Reproduction and Expansion of \\"SPECIALIZATION TRENDS IN ECONOMICS RESEARCH" by Sebastian Galiani, Ramiro H. Gálvez, and Ian Nachman

### 2025-02-18 documents/paper.tex
Update to pixi environment.
Initial commit of analysis.
Clean JEL codes for further analysis.

@@

>>>>

\section{Introduction}

\section{Data}

\subsection{Data Collection and Cleaning}

@@

These 15 entries are excluded from the analysis.

Dropped 18 entries, that have been superseded by another discussion paper.

Dropped one discussion paper each with the JEL Codes "workfromhomecommutetimesallocationoftimesavingsCOVID19" (15870), and
"labordisplacementenergytransitioncoalmines" (15581).
Dropped 16 discussion papers due to completely missing JEL Codes, these were from March 2024 to February 2025.
There were about 45 discussion papers that needed manual attention to fix the extracted JEL Codes.
Likely the JEL Codes were extracted on IZA side via Optical Character Recognition (OCR) from the PDFs, leading to confusions of e.g. "I" and "1" or "O" and "0".
